---
  output: 
    word_document:
      reference_docx: mystyles.docx
---
  
```{r echo=FALSE}
library(knitr) 
# See https://stackoverflow.com/questions/28331343/knitting-to-pdf-in-r for info

#arch <- read.csv("../data/archetype_summary.csv" , stringsAsFactors = FALSE)
#i = 1

#Make the Archetype Table

archtable <- data.frame(Description = c("Building Type",
                                   "Wall Construction",
                                   "Roof Type",
                                   "Energy System"), 
                         Value = c(arch$arch_type[i],
                                  arch$arch_wall[i],
                                  arch$arch_roof[i],
                                  arch$arch_energy[i]),
                         Descriptions = c("Double Glazing", 
                                   "Floor Construction", 
                                   "Solar Suitable", 
                                   ""), 
                         Values = c(arch$arch_window[i],
                                  arch$arch_floor[i],
                                  arch$arch_solar[i],
                                  ""))


#Make the Dimensions Summary Table
dimensions <- data.frame(Description = c("Number of Floors",
                                   "Floor Area (m2)",
                                   "Plan Roof Area (m2)",
                                   "Slope Roof Area (m2)",
                                   "Ground Floor Ceiling Height (m)"), 
                         Value = c(paste0(arch$nfloors.Q1[i]," - ",arch$nfloors.Q3[i]),
                                  paste0(arch$floorarea.Q1[i]," - ",arch$floorarea.Q3[i]),
                                  paste0(arch$roofareaplan.Q1[i]," - ",arch$roofareaplan.Q3[i]),
                                  paste0(arch$roofareaslope.Q1[i]," - ",arch$roofareaslope.Q3[i]),
                                  paste0(arch$ceilingground.Q1[i]," - ",arch$ceilingground.Q3[i])),
                         Descriptions = c("External Wall Area (m2)", 
                                   "Internal Wall Area (m2)", 
                                   "DPC Perimeter (m)", 
                                   "Estimated Useful Solar Area (m2)",
                                   "First Floor Ceiling Height (m)"), 
                         Values = c(paste0(arch$extwallarea.Q1[i]," - ",arch$extwallarea.Q3[i]),
                                  paste0(arch$intwallarea.Q1[i]," - ",arch$intwallarea.Q3[i]),
                                  paste0(arch$dpcperim.Q1[i]," - ",arch$dpcperim.Q3[i]),
                                  paste0(arch$solararea.Q1[i]," - ",arch$solararea.Q3[i]),
                                  paste0(arch$ceilingfirst.Q1[i]," - ",arch$ceilingfirst.Q3[i])) )

#Make doors and windows table
windows <- data.frame(Description = c("Number of Windows", "Number of External Doors"), 
                         Value = c(paste0(arch$windows.Q1[i]," - ",arch$windows.Q3[i]),
                                   paste0(arch$doors.Q1[i]," - ",arch$doors.Q3[i])),
                         Descriptions = c("Window Area (m2)", 
                                   ""), 
                         Values = c(paste0(arch$extwindowarea.Q1[i]," - ",arch$extwindowarea.Q3[i]),
                                  ""))


#Make the Locations Summary Table
locations <- data.frame(locations = c("city centre","other urban centre","suburban residential","rural residential","village centre","rural"), val = c(arch$citycentre[i], arch$otherurban[i], arch$suburban[i], arch$ruralres[i], arch$villagecentre[i], arch$rural[i]))
locations <- locations[locations$val >0,]
locations <- locations[order(-locations$val),]
locations$percent <- round(locations$val / sum(locations$val) * 100, 0)
locations$val <- NULL
locations <- locations[1:2,]



#Make Tennacy table
Tenancy <- data.frame(Tenancy = c("Owner Occupy","Private Rent","LA Rent","RSL Rent"), 
                      val = c(arch$own[i],arch$rent.private[i],arch$rent.la[i],arch$rent.rsl[i]))
Tenancy <- Tenancy[Tenancy$val >0,]
Tenancy <- Tenancy[order(-Tenancy$val),]
Tenancy$percent <- round(Tenancy$val / sum(Tenancy$val) * 100, 0)
Tenancy$val <- NULL
Tenancy <- Tenancy[1:2,]

#Make the Genral Summary Table
summary <- data.frame(Description = c("Built between",
                                     "SAP Energy Rating",
                                     ""
                                     ),
                      Value = c(paste0(arch$age.Q1[i]," - ",arch$age.Q3[i]),
                                paste0(arch$sap.Q1[i]," - ",arch$sap.Q3[i]),
                                ""
                                ),
                      Descriptions = c("Heating Controls",
                                       "Radiator Controls",
                                      "% with access to mains gas"
                                      ),
                      Values = c(paste0(arch$control.Q1[i]," - ",arch$control.Q3[i]),
                                 paste0(arch$radcontrol.Q1[i]," - ",arch$radcontrol.Q3[i]),
                                 arch$gasgrid.yes[i]
                                 )
                      
                      
                      )



```


# `r arch$archcode[i]`

`r formatC(arch$ndwel[i], format = "d", big.mark = ",")` dwellings based on `r formatC(arch$nsample[i], format = "d", big.mark = ",")` samples from the English Housing Survey 2013

This archetype is characterised by:

```{r echo=FALSE}
kable(archtable, row.names = FALSE)
```

Dwellings of this archetype have the following typical existing characteristics. Values show the inter quartile range i.e. 50% of dwellings are between the two values shown.

## Summary
```{r echo=FALSE}
kable(summary, row.names = FALSE)
```

## Dimensions
```{r echo=FALSE}
kable(dimensions, row.names = FALSE)
```

## Windows
```{r echo=FALSE}
kable(windows, row.names = FALSE)
```


##Most Common Tenancies & Most Common Locations
```{r echo=FALSE}
kable(cbind(Tenancy,locations), row.names = FALSE)
```

##Retrofit Progress Information

Dwellings with insulated  walls: `r arch$wallins[i]` %

Dwellings with well insulated lofts: `r arch$loftins[i] ` %

Dwellings with well inuslated hot water tanks: `r arch$tank.wellins[i]` %

